Binocular combination in the autonomic nervous system

### 2024-05-22 manuscript.Rmd
Revert to standard settings

domodelling <- 1    # if set to 1, run the Stan models (takes ~24 hours)

@@

# settings for sampler 
numSavedSteps <- 100000/100    # total number of MCMC steps
adaptSteps <- 1000/10  # Number of steps to "tune" the samplers
burnInSteps <- 2000/10
thinSteps <- 10/10
nChains <- 16/4
ncores <- 8/8
options(mc.cores=ncores)

>>>>

domodelling <- 0    # if set to 1, run the Stan models (takes ~24 hours)

@@

# settings for sampler 
numSavedSteps <- 100000    # total number of MCMC steps
adaptSteps <- 1000  # Number of steps to "tune" the samplers
burnInSteps <- 2000
thinSteps <- 10
nChains <- 16
ncores <- 8
options(mc.cores=ncores)
